Estimating duration in the presence of misclassification

### 2024-01-04 cis-imperfect-testing.tex
Figures with imperfect testing results

Applying the method of \cref{E-perf-test} to CIS data gives implausible estimates of the duration distribution (see \cref{imperf-test:fig:problem-cis-estimates}).
In particular, it estimated a much shorter duration of positivity than in \cref{E-ATACCC}, despite those estimates being much more reliable over the first 2--3 weeks.
\begin{figure}
  \centering %\includegraphic{}
  \todo[inline]{Figure showing estimates without false negatives}
  \caption[Estimating survival using CIS data assuming perfect testing]{Estimating the survival function using CIS data and the model of \cref{E-perf-test} gives implausibly short estimates. \label{imperf-test:fig:problem-cis-estimates}}
\end{figure}

@@

With this prior, the model produces plausible estimates of the duration distribution (see \cref{imperf-test:fig:cis-estimates}).
This estimate has more long episodes than the estimate in \cref{E-ATACCC}.
The qualitative increase in long episodes is robust to the choice of prior for $\ntot$, the assumed value for $\psens$ (see \cref{imperf-test:fig:cis-sensitivity}), and the choice of prior for $\lambda$.
However, the survival proportion over the first 4 weeks is sensitive to these choices.
The estimate using a test sensitivity of 0.8 and $\NBc(\numprint{25132}, \numprint{22047})$ give a median survival time most similar to that of \cref{E-ATACCC}.
\begin{figure}
  \todo[inline]{Insert fig showing final estimate and comparison to ATACCC}
  \caption{Duration estimates using CIS and ATACCC data}
  \label{imperf-test:fig:cis-estimates}
\end{figure}
\begin{figure}
  \todo[inline]{
    Insert figs showing, for different assumption:
    proportion of individuals still positive at day 30 or 50 (tail),
    overall survival curve, and
    median survival time (in comparison to ATACCC).
  }
  \caption{Sensitivity of CIS estimates to assumptions}
  \label{imperf-test:fig:cis-sensitivity}
\end{figure}

>>>>

Applying the method of \cref{E-perf-test} to CIS data gives implausible estimates of the duration distribution (see \cref{imperf-test:fig:problem-cis-estimates}).
In particular, it estimated a much shorter duration of positivity than in \cref{E-ATACCC}, despite those estimates being much more reliable over the first 2--3 weeks.
\begin{figure}
  \centering \includegraphics{cis-imperfect-testing/CIS_perfect}
  \caption[Estimating survival using CIS data assuming perfect testing]{Estimates of the survival function using CIS data alongside the ATACCC-based estimates of \cref{E-perf-test}. CIS-based is implausibly short over the first 14 days. \label{imperf-test:fig:problem-cis-estimates}}
\end{figure}

@@

With this prior, the model produces plausible estimates of the duration distribution (see \cref{imperf-test:fig:cis-estimates}).
This estimate has more long episodes than the estimate in \cref{E-ATACCC}.
The qualitative increase in long episodes is robust to the choice of prior for $\ntot$, the assumed value for $\psens$ (see \cref{imperf-test:fig:cis-sensitivity}), and the choice of prior for $\lambda$.
However, the survival proportion over the first 4 weeks is sensitive to these choices.
The estimate using a test sensitivity of 0.8 and $\NBc(\numprint{25132}, \numprint{22047})$ give a median survival time most similar to that of \cref{E-ATACCC}.
\begin{figure}
  \centering \includegraphics{cis-imperfect-testing/CIS_final}
  \caption{Duration estimates using CIS and ATACCC data}
  \label{imperf-test:fig:cis-estimates}
\end{figure}
\begin{figure}
  \vspace{-2.5cm}
  \makebox[\textwidth][c]{\includegraphics{cis-imperfect-testing/CIS_vary}}
  \caption{%
    Sensitivity of CIS estimates to: (A-C) the value of $r$ in the prior for $\ntot$ and (D-F) $\psens$.
    A and D: median survival time, in comparison to the ATACCC-based estimate of \cref{E-ATACCC}.
    B and E: survival at day 50, $S_\theta(50)$.
    C and F: full survival curves out to day 100.
  }
  \label{imperf-test:fig:cis-sensitivity}
\end{figure}
